Modelling low Mach number stellar hydrodynamics with MAESTROeX

### 2019-10-02 astronum_2019_MAESTROeX/astronum-maestroex.tex

\begin{figure}\label{fig:gpu_speedup}
    \centering

    \includegraphics[width=\textwidth]{plots/gpu_speedup}

    \caption{Comparison of the performance of functions on the CPU vs the GPU. The plot shows the average execution time for several functions, recorded for a run of the three-dimensional \texttt{reacting\_bubble} problem on Summit. Both tests were performed using a single node, with the CPU test using 42 MPI processes, each with 4 OpenMP threads, and the GPU test using 6 MPI processes, each process associated with a single GPU. Note that the $x$-axis scale is logarithmic.}

\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{plots/gpu_speedup}
    \caption{Comparison of the performance of functions on the CPU vs the GPU. The plot shows the average execution time for several functions, recorded for a run of the 3d \texttt{reacting\_bubble} problem on Summit. Both tests were performed using a single node, with the CPU test using 42 MPI processes, each with 4 OpenMP threads, and the GPU test using 6 MPI processes, each process associated with a single GPU. Note that the $x$-axis scale is logarithmic.}\label{fig:gpu_speedup}
\end{figure}
